Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-10-20 text/ms.tex
Add supp material note

>>>>

\section{Supplementary Material}

The following supplementary material is available online for this article:\\
Figures S1--S11\\
Table S1\\
Example Stan code for a heavy-tailed Gompertz model and multilevel beta
regression\\
The GPDD IDs used in our analysis\\
All code and data to recreate our analysis is available at:\\
\url{https://github.com/seananderson/heavy-tails}
